\section{Simulating a Pareto Distribution}
```{r}
library("VGAM")
```

\subsection{First Moment with Monte Carlo}

Given a a random variable distributed $X \sim Par(2.5, 1)$ which density is:

\begin{equation}
F_X(x) =
\left\{
	\begin{array}{ll}
		\frac{5}{2}x^{-\frac{7}{2}} &   \mbox{if  } x \geq 1 \\
		0                           &   \mbox{if  } x < 1 
	\end{array}
\right.
\end{equation}

Which graph is:

```{r}
x <- seq(from=1, to=100, by=0.01)
curve(dpareto(x, shape=2.5, scale=1), xlim = c(0,10), ylim=c(0,3), type="l", main="Pareto Distribution",
     ylab="density", col="red")
```

Since this is a well known distribution, of which first moment is easily computable in closed form, is intresting to check how closely a Monte Carlo simulation is able to estimate the exact parameter. 

In order to do this we have two options:

\begin{enumerate}
\item Generate a random sample from R-Cran Built in Pareto distribution
\item Use the Inverse Transform Method, using a Uniform Distribution as instrumental function
\end{enumerate}

However, in advance to any techinque we need to know, exploiting the LLN, how many samples we need in order to estimate with a confidence of $10^-2$ the mean.

The first option is pretty straightfoward since we can use R built in function:

```{r}
first <- rpareto(85000, shape=2.5, scale=1)
I_hat = mean(first)
I_hat
```
The second one consist in  the Integral Transform Method which using the inverse function of the Pareto and a Uniform RNG allows us to sample from a pareto:

Since $Par(2.5,2)$ first moment is given by, we can see how the two approaches compares:


\subsubsection{Empirical Distribution vs Desired Target Distribution}

Now that can also check two different EDF and see that the while qualitatively there is no much difference between the two approaches, from a efficiency point of view there two order of magnitude slower.
