\section{Simulating a Pareto Distribution}
```{r}
library("VGAM")
```

\subsection{First Moment with Monte Carlo}

Given a a random variable distributed $X \sim Par(2.5, 1)$ which density is:

\begin{equation}
F_X(x) =
\left\{
	\begin{array}{ll}
		\frac{5}{2}x^{-\frac{7}{2}} &   \mbox{if} & x \geq 1 \\
		0                           &   \mbox{if} & x < 1 
	\end{array}
\right.
\end{equation}

Which graph is:

```{r}
x <- seq(from=1, to=100, by=0.01)
first <- rpareto(900000, shape=2.5, scale=1)
curve(dpareto(x, shape=2.5, scale=1), xlim = c(0,10), ylim=c(0,3), type="l", main="Pareto Distribution",
     ylab="density", col="red")
```

Since this is a well known distribution, of which first moment is easily computable in closed form, is intresting to check how closely a Monte Carlo simulation is able to estimate the exact parameter. 

In order to do this we have two options:

\begin{enumerate}
\item Generate a random sample from R-Cran Built in Pareto distribution
\item Use the Inverse Transform Method, using a Uniform Distribution as instrumental function
\end{enumerate}

The first option is pretty straightfoward since we can use R built in function:

```{r}
#curve(first, xlim=c(0,10))
I_hat = mean(first)
I_hat
```


\subsubsection{Approximate first moment up to precision $10^{-2}$}

\subsubsection{Running Mean}

\subsubsection{Empirical Distribution vs Desired Target Distribution}



\textbf{Definition 1.1} A \textit{parametric space} is the set of all possible combinations of values for all the different parameters contained in a particular mathematical model 

Given the previous definition the parametric space of interest, which is the probability of success of a single event, is $\Theta \in [0,1]$