---
title: "Random Algorithms for Random Things"
author: "Benedetto Jacopo Buratti - Homework I"
date: "January 12, 2017"
output: 
  pdf_document: 
    latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
\abstract
This first homework covers the main concepts behind bayesian inference and some related issues. In the \textbf{first} and \textbf{second} exercises we focus on conjugate analysis, a classical approach to bayesian inference, used in the special occasion where the posterior distribution has the same distribution of the likelihood function. In the \textbf{third} and \textbf{fourth} exercise we introduce the Integral Transformation Formula, which will be the core, with unifrom pseudo-random numer generator of exercises \textbf{fifth} and \textbf{sixth} Finally in the \textbf{seventh}, \textbf{eighth} and \textbf{nineth} exerices we introduce and use the acceptance and rejection algorithm and apply in in a variety of situations.  

<!--
\begin{enumerate}
\item Fundamental ingredients to carry out Bayesian Inference
\item Dugongs: frequentist vs bayesian approach
\item Introduction and application of the Integral Transformation Method (ITF)
\item Mean and varaince of a transfromed distribution
\item Generate a sequence of i.i.d random veviates with a Pareto distribution from a Uniform one (using ITF)
\item Generate a sequence of i.i.d random veviates with a discrete distribution from a Uniform one (using ITF) 
\item Simulate from a Beta(3,3) using Acceprance-Rejection algorithm.
\item General Acceprance-Rejection algorithm
\item Generate from a Normal distribution from a Cauchy distribution using A/R 
\end{enumerate}
-->
\tableofcontents


\newpage
```{r child = 'chapter1.Rmd'}
```
\newpage
```{r child = 'chapter2.Rmd'}
```
\newpage
```{r child = 'chapter3.Rmd'}
```
\newpage
```{r child = 'chapter4.Rmd'}
```
\newpage
```{r child = 'chapter5.Rmd'}
```
\newpage
```{r child = 'chapter6.Rmd'}
```
\newpage
```{r child = 'chapter7.Rmd'}
```
\newpage
```{r child = 'chapter8.Rmd'}
```
\newpage
```{r child = 'chapter9.Rmd'}
```
