\section{Puppet Markov Chain}

First of all let's define the Markov Chain that we want to analyze:

\begin{figure}
   \includegraphics[width=0.475\textwidth]{images/markov.png}
   \hfill
   \includegraphics[width=0.475\textwidth]{images/markov.png}
   \caption{On the left the graphical reppresentaion of our Markov Chain and on the right its transition matrix}
\end{figure}



First of all we define a s4 object constructor for Markov Chains and than delcare an puppet markov chain:

```{r, include = TRUE}
#Markov Chains Constructor

setClass("markov_chain",
         slots = list(state_space="numeric",
                      initial_state="numeric",
                      chain_size="numeric",
                      transition_matrix="matrix"))
```

\subsection{Markov Chain Simulation}

We now define a function that would allows us to simulate our chain

```{r, include = TRUE}
#Markov Chain Simulator

setMethod("simulate", signature("markov_chain"), function(object){
  markov_chain <- c(vector(), 1:(object@chain_size+1))
  markov_chain[1] = object@initial_state
  
  for(t in 1:object@chain_size){
    markov_chain[t+1] <- sample(object@state_space, size = object@chain_size, prob=object@transition_matrix[markov_chain[t],], replace = TRUE)
  }
  return(markov_chain)
})
```

Now that the we have all the necessary elements we can simulate our markov chain:

```{r, include=TRUE}

puppet_markov_chain <- new("markov_chain",
                           state_space = c(1,2,3),
                           initial_state = 1,
                           chain_size = 1000,
                           transition_matrix = matrix(c(0, 1/2, 1/2, 5/8, 1/8, 1/4, 2/3, 1/3, 0), nrow = 3, ncol = 3)
                           )

puppet_markov_chain

print(simulate(puppet_markov_chain))
```
\subsection{States Empirical Relative Frequency}

\subsection{Simulation Repeatition}


\subsection{Invariant Distribution $\pi$ (closed form)}

\subsection{Evaluation}

\subsection{Initial State Independecy}

